Understanding Broadway Gross: Key Factors and Growth Strategies

### 2024-12-02 paper/paper.qmd
Refine the paper, adding references and relevant literature
Revise the paper by adding a more detailed caption, refining the estimand, and improving the discussion section. Enhance the abstract and findings by incorporating specific numbers and results from the study.

---
title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
subtitle: "Positive Effects of Pricing, Seats, Performances, and Holidays, with Limited Impact During Tony Award Months"
author: "Xuanel Zhou"
thanks: "Code and data are available at:https://github.com/Isazhou13/Broadway_Gross"
date: today
date-format: long
toc: true
abstract: "This study examines the key factors influencing Broadway’s weekly gross revenue using datasets from Playbill and The Broadway League. The result shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact gross, while Tony Award months show limited effects. Despite steady long-term growth, disruptions such as the 2016 snowstorm and COVID-19 highlight the industry’s vulnerability to external shocks. These findings provide actionable strategies, including holiday-focused marketing, and enhanced engagement during award seasons, to sustain growth and optimize Broadway’s financial performance."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Broadway is a cultural and economic landmark in New York City, contributing significantly to the city's global reputation and economy. For stakeholders, understanding the drivers of Broadway revenue is essential, as it directly informs strategic decisions on pricing, scheduling, and resource allocation to maximize profitability and sustain operations. This study aims to identify and quantify the key factors influencing Broadway’s weekly gross revenue, using datasets provided by Playbill and The Broadway League.

The estimand in this paper represents the weekly gross revenue of Broadway shows. Specifically, it examines how variables such as ticket price, theater seating capacity, number of performances, whether it is a holiday week, whether it falls in a Tony Award month, and the year influence weekly gross revenue. While the true estimand is unknown, it is approximated using the available data and model assumptions. Defining the estimand ensures the model and methodology align with the research objective and facilitates addressing potential biases from data limitations or methodological choices.

The analysis, conducted using a multiple linear regression model, shows that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway’s weekly gross revenue. Conversely, the limited impact of Tony Award months highlights opportunities for growth. While steady long-term growth is observed, disruptions such as the 2016 snowstorm and COVID-19 emphasize Broadway’s vulnerability to external shocks.

These findings emphasize both the opportunities and challenges Broadway faces in maximizing its revenue. Identifying the factors that drive revenue and highlighting periods of underperformance provide a foundation for adapting to evolving market conditions. For instance, additional potential can be realized through strategies such as holiday packages, collaborations with tourism boards, and enhanced on-site experiences. To address the low impact of Tony Award months, strategies could include offering exclusive ticket packages and enhancing media engagement to capitalize on the event's visibility. In an era of rapid digitalization and shifting consumer preferences, Broadway must innovate and adopt targeted strategies to sustain growth and maintain its position as a global cultural icon.

The remainder of this paper is structured as follows: @sec-data provides an overview of the dataset and visualizations of the variables. @sec-model-set-up details the modeling approach, including predictor selection and the regression model structure. @sec-results presents the primary findings and outcomes of the model. Finally, @sec-discussion explores the key findings, highlights the main takeaways, addresses the study's weaknesses, and outlines potential next steps.

@@

The dataset, sourced from **Playbill**, reflects Broadway weekly grosses as reported by theatres affiliated with The Broadway League. The data cleaning process involved grouping observations and removing missing values. The final dataset consists of 14,519 observations across 10 variables: `week_ending`, `week_number`, `weekly_gross`, `avg_ticket_price`, `seats_in_threatre`, `performances`, `year`, `month`, `holiday_week` and `Tony_Award`.

@@

The dataset for this study originates from Playbill, which collects information about Broadway shows through direct reporting and partnerships with industry organizations. A significant portion of the data, particularly box office grosses and performance metrics, is provided by The Broadway League, a national trade association for the Broadway industry.

The transformation of real-world phenomena into the dataset begins with data collection. The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information. Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records. This information is then processed into key metrics, including ticket sales, attendance, revenue, and theater utilization, which are published weekly. Before release, The League’s research department verifies the data’s accuracy and removes personal information to ensure privacy.

@@

```{r}
#| label: fig-weekly_gross
#| fig-cap: Distribution of Broadway weekly gross.
#| echo: false

@@

The outcome variable of interest for this study is the weekly gross revenue for Broadway productions. The distribution, shown in @fig-weekly_gross, exhibits a right-skewed pattern. Most weeks have revenues ranging between $500,000 and $2,000,000, with a declining frequency as revenue increases. The mode of the distribution appears around $2,000,000. A small number of weeks report revenues exceeding $3,000,000, which may represent potential outliers or rare events that warrant further investigation. These high-revenue weeks could stem from unusual circumstances, such as special promotions, holiday seasons, or significant market shifts.

@@

```{r}
#| label: fig-yearly
#| fig-cap: Yearly Gross Revenue Trends for Broadway Productions, spanning from 2010 to 2019.
#| echo: false
#| warning: false
#| message: false

@@

# Create the plot
ggplot(data_yearly, aes(x = year, y = average_weekly_gross)) +
  geom_line(color = "steelblue", size = 1) +
  labs(
    x = "Year",
    y = "Average Yearly Gross ($)"
  ) +
  theme_minimal() +
  scale_x_continuous(  # Adjust scale for years
    breaks = seq(min(data_yearly$year), max(data_yearly$year), by = 1),  # One tick per year
    labels = scales::label_number(accuracy = 1)  # Show integer year labels
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.subtitle = element_text(hjust = 0.5, size = 12)
  )

@@

```{r}
#| label: fig-week_ending
#| fig-cap: Weekly grossfor each Broadway show over time, spanning from 2010 to 2019. Each point represents the gross for a particular week for a specific show.
#| echo: false
#| warning: false
#| message: false

@@

```
@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $500,000 to $2,000,000, which aligns with the histogram results shown in @fig-weekly_gross. However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.

@@

```{r}
#| label: fig-avg_ticket_price
#| fig-cap: Distribution of Average Broadway Ticket Prices
#| echo: false

@@

```{r}
#| label: fig-seats_in_theatre
#| fig-cap: Distribution of Theatre Sizes Based on Number of Seats
#| echo: false

@@

```{r}
#| label: fig-performances
#| fig-cap: Distribution of Performances
#| echo: false

@@

```{r}
#| label: fig-holiday_week
#| fig-cap: Comparison of Average Weekly Gross Between Holiday and Non-Holiday Weeks
#| echo: false

@@

# Bar chart for average weekly gross
ggplot(aggregated_data_holiday, aes(x = holiday_week, y = avg_weekly_gross, fill = holiday_week)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```
Holiday weeks were identified based on the major holidays of the year and include the following:
New Year’s Week: The week containing January 1st.

- Independence Day Week: The week of July 4th.
- Labor Day Week: The week containing Labor Day, which falls on the first Monday of September.
- Thanksgiving Week: The week containing the fourth Thursday of November.
- Christmas Week: The week containing December 25th.
- New Year's Week: The week of the January 1st.

Non-holiday weeks are defined as all other weeks that do not overlap with these predefined holiday periods.

The weekly gross revenue was aggregated by grouping the data into holiday and non-holiday weeks. The average weekly gross revenue for each category was then calculated by summing all weekly gross revenues within the category and dividing by the total number of weeks in that category.

@@

```{r}
#| label: fig-Tony_Award
#| fig-cap: Comparison of Weekly Gross Revenue During Tony Award and Non-Award Months
#| echo: false

@@

# Bar chart for average weekly gross
ggplot(aggregated_data_award, aes(x = Tony_Award, y = avg_weekly_gross, fill = Tony_Award)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    title = "Average Weekly Gross for Holiday vs Non-Holiday Weeks",
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```
The Tony Awards, formally the Antoinette Perry Award for Excellence in Broadway Theatre, are the highest honors in Broadway, typically held in June to mark the end of the Broadway season. Due to COVID-19, the 2020 awards were postponed to September.

@@

The objective of this study is to assist Broadway in strategically managing and making decisions to increase gross revenue, making it essential to choose a model that accurately explains the factors influencing revenue.To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.

@@

Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

- Intercept ($\beta_0$): Represents the predicted value of the weekly gross revenue when all predictors are 0. Since it is unrealistic for all predictors the intercept serves as a theoretical starting point for the model. 
- Average Ticket Price ($\beta_1$): Measures the change in weekly gross revenue for each one-unit increase in average ticket price, assuming other predictors remain constant.
- Seats in the Theater ($\beta_2$):Represents the additional revenue associated with a one-unit increase in the seating capacity of the theater, holding other factors constant.
- Number of Performances ($\beta_3$): Indicates the increase in weekly gross revenue for each additional performance in the week, controlling for other variables.
- Holiday Week ($\beta_4$): Quantifies the difference in weekly gross revenue between holiday weeks and non-holiday weeks, all else being equal.
- Tony Award Month ($\beta_5$): Captures the difference in weekly gross revenue between weeks during the Tony Award month and other months, assuming other predictors remain unchanged.
- Year ($\beta_6$): Reflects the annual trend, representing the average change in weekly gross revenue for each one-year increase, controlling for other variables.

@@

As anticipated, average ticket price, seating in yheater, and number of performances exhibit significant positive relationships with weekly gross revenue. Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth. Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences.

@@

## Balancing Pricing, Seating Capacity, and Performance Frequency

Operational strategies such as ticket pricing, seating capacity, and performance frequency emerged as key drivers of weekly gross revenue, offering actionable opportunities for Broadway to increase earnings. The strong impact of average ticket price underscores the importance of implementing demand-based pricing strategies, particularly for popular or limited-run productions, where higher ticket prices can significantly boost revenue with minimal impact on attendance. For less popular shows, optimizing affordability could help maintain audience retention while still contributing to overall revenue.

Maximizing theater utilization through strategic scheduling and venue allocation is key to increasing revenue. Larger venues and additional performances can expand audience capacity, but Broadway managers must evaluate whether demand can sufficiently meet the increased supply. Additionally, managers must balance these strategies with logistical considerations such as performer availability, production costs, and preserving the quality of the audience experience. By carefully aligning pricing strategies with capacity optimization, Broadway can enhance revenue while ensuring sustainable long-term growth.

## Opportunities in Holiday Weeks and Tony Award Months

The model results indicate that while holiday weeks align with the expectation of increased revenue due to higher audience availability, the effects of Tony Award months challenge the assumption that they inherently boost revenue through increased media attention.

During holiday weeks, families often travel or engage in special outings. New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, holiday markets, and the New Year’s Eve Ball Drop in Times Square. This festive atmosphere draws millions of tourists, creating a significant opportunity for Broadway to boost gross revenue and position itself as a must-visit holiday experience.

To fully utilize its prime location, Broadway could implement targeted strategies to make attending shows more convenient and attractive for holiday visitors. For example, collaborating with hotels, travel agencies, and tourism boards to create holiday packages that include show tickets could firmly establish Broadway as an essential part of the holiday itinerary. Additionally, enhancing the on-site experience with seasonal concessions and festive elements could further help Broadway attract more visitors during this lucrative season.

For Tony Award months, the data indicates that Broadway gross remains unaffected, challenging the belief that the awards inherently drive revenue through increased media attention. While the Tony Awards generate significant publicity, the focus tends to be on a limited number of nominated or winning shows, leaving many other shows relatively unnoticed. This concentrated attention may not translate into broader attendance increases across the industry. To address this, Broadway could collaborate with media outlets to feature live broadcasts, behind-the-scenes content, and interviews with nominees to create excitement around both the awards and the shows themselves. Offering exclusive ticket packages for Tony-nominated shows during the awards season could further incentivize attendance and increase revenue.

## Sustaining Broadway’s Growth in the Changing World

The significant positive relationship between year and weekly gross revenue reflects the steady growth of Broadway over the past decade, driven by factors such as rising ticket prices, increased tourism, and the industry’s ability to attract global audiences. However, this growth trajectory also have some exceptional cases, and not valid for all time period. For instance, the sharp decline in 2016 weekly gross during winter was influenced by a severe snowstorm that forced theaters to close, disrupting public transportation and preventing both audiences and performers from attending. Similarly, the slight downturn in 2019 coincided with the onset of the COVID-19 pandemic, which led to theater closures, halted performances, and a collapse in ticket sales, exposing Broadway’s reliance on in-person attendance and its vulnerability to external disruptions.

Even with a generally positive and sustainable long-term growth trend, Broadway must adapt and innovate to keep pace with the rapid changes in today’s society. The rise of streaming platforms and the growing popularity of short-form video content present new challenges to live theater, demanding fresh approaches to attract and engage modern audiences. By embracing digital innovations while emphasizing the unique, immersive experience of live performances, Broadway can maintain its growth and continue thriving as a global cultural hub.

@@

Additionally, the model assumes uniform effects of predictors across all Broadway shows, which may oversimplify the analysis. Different types of productions (e.g., musicals, plays, blockbusters, or niche shows) likely have distinct revenue dynamics that are not adequately addressed by a single model.

Moreover, the model does not account for external factors such as economic conditions, competitor pricing, or shifts in tourism trends, all of which could significantly influence Broadway revenue. These omissions limit the model's ability to fully explain variations in weekly gross revenue and highlight areas for future improvement.

@@

Have you seen this show before?

- Yes
- No

@@

@@

In addition to the dataset used for this study, Broadway conducts several key surveys to collect detailed information on various aspects of Broadway theater. However, the information and datasets collected through these surveys are not publicly accessible for analysis. If this data were made available, merging it with the current dataset could provide a more robust model for gross analysis. These surveys include **The Demographics of the Broadway Audience**, designed to analyze the composition and behavior of Broadway theatergoers.

@@

Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway. These surveys and studies provide a broader understanding of Broadway's influence and reach, offering a more complete view of its cultural and economic significance.

>>>>

---
title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
subtitle: "Optimizing Revenue Per Seat While Addressing Modest Holiday Gains and Revenue Declines in Tony Award Months"
author: "Xuanel Zhou"
thanks: "Code and data are available at: [Broadway_Gross](https://github.com/Isazhou13/Broadway_Gross)."
date: today
date-format: long
toc: true
abstract: "This study employs multiple linear regression to examine factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months. A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity. Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge reveals untapped potential for Broadway to enhance its appeal as a premier holiday destination. Conversely, Tony Award months are linked to a $7,140 decline in weekly revenue, highlighting the need to reposition the awards season as an industry-wide promotional opportunity to benefit all productions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Broadway, located in the heart of New York City's Theater District, comprises 41 theaters in Midtown Manhattan, extending from 42nd to 53rd Streets and between 6th and 8th Avenues [@broadway2021]. Renowned as a cultural and economic landmark, Broadway plays a pivotal role in shaping the city's global reputation and driving its economy. For stakeholders, understanding the drivers of Broadway revenue is essential, as it directly informs strategic decisions on pricing, scheduling, and resource allocation to maximize profitability and sustain operations. This study seeks to identify and quantify the key factors influencing Broadway’s weekly gross revenue, utilizing datasets created by Alex Cookson [@cookson_broadway_grosses], which are derived from data originally provided by Playbill [@playbill_grosses].

The estimand of interests in this study is the average change in weekly gross revenue for Broadway productions associated with specific predictors, including ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months, while holding other factors constant. This measure captures the independent impact of each variable on revenue. While the true estimand is inherently unknown due to potential unobserved confounders, it is approximated using multiple linear regression, relying on the available data and model assumptions. Clearly defining the estimand ensures the analysis aligns with the research objectives, facilitates interpretation of the relationships between predictors and revenue, and addresses potential biases from factors such as omitted variables or measurement errors, ensuring the findings remain meaningful and relevant for revenue optimization.

The analysis reveals that ticket pricing, seating capacity, performance frequency, and holiday weeks positively impact Broadway's weekly gross revenue. Specifically, each additional performance generates $70,688, while holiday weeks add $16,684 to weekly revenue. Conversely, Tony Award months are associated with a $7,240 decline in weekly gross revenue, underscoring the need to adjust strategies to better capitalize on this period.

These findings highlight both the opportunities and challenges Broadway faces in maximizing its revenue. Prioritizing revenue per seat over simply increasing seating capacity offers a more effective approach to boosting Broadway's financial performance. Additionally, significant potential can be unlocked through strategies such as holiday packages, partnerships with tourism boards, and enhancing the on-site experience with festive offerings and merchandise. To address the negative impact of Tony Award months, initiatives exclusive ticket bundles, targeted promotions, and expanded media engagement can help capitalize on the event’s visibility.

The remainder of this paper is structured as follows: @sec-data provides an overview of the dataset and visualizations of the variables. @sec-model-set-up details the modeling approach, including predictor selection and the regression model structure. @sec-results presents the primary findings and outcomes of the model. Finally, @sec-discussion explores the key findings, highlights the main takeaways, addresses the study's weaknesses, and outlines potential next steps. @sec-Appendix1 contains the idealized survey designed to gather more detailed information, while @sec-Appendix2 provides supplementary information about the current dataset. Lastly, @sec-model includes diagnostic analyses of the model.

@@

The dataset, compiled by Alex Cookson [@cookson_broadway_grosses] and derived from data originally provided by Playbill [@playbill_grosses], represents Broadway's weekly grosses. The data cleaning process involved grouping observations and removing missing values. The final dataset consists of 14,519 observations across 9 variables: `week_number`, `weekly_gross`, `avg_ticket_price`, `seats_in_threatre`, `performances`, `year`, `month`, `holiday_week` and `Tony_Award`. The dataset used for this analysis spans from the beginning of 2010 to the end of 2019.

@@

The dataset for this study originates from Playbill [@playbill_grosses], which collects information about Broadway shows through direct reporting and partnerships with industry organizations. A significant portion of the data, particularly box office grosses and performance metrics, is provided by The Broadway League [@broadway_statistics], a national trade association for the Broadway industry.

The transformation of real-world phenomena into the dataset begins with data collection. The Internet Broadway Database (IBDB), maintained by The Broadway League, compiles detailed records of Broadway productions using sources like theater programs to document cast and crew information [@ibdb_about]. Additional data is supplemented by newspaper and magazine reports, theatrical textbooks, interviews with theater professionals, and The League's archival records. This information is then processed into key metrics, including ticket sales, attendance, revenue, and theater utilization, which are published weekly. Before release, The League’s research department verifies the data’s accuracy and removes personal information to ensure privacy.

@@

```{r}
#| label: fig-weekly_gross
#| fig-cap: Distribution of Broadway weekly gross. Weekly gross revenues predominantly fall between $500,000 and $2,000,000, with the largest concentration near $700,000 and few instances surpassing $3,000,000.
#| echo: false

@@

The outcome variable of interest for this study is the weekly gross revenue for Broadway productions. The distribution, shown in @fig-weekly_gross, exhibits a right-skewed pattern. Most weeks have gross revenue ranging between $500,000 and $2,000,000, with a declining frequency as revenue increases.  with the highest frequency observed around $700,000. A small number of weeks report revenues exceeding $3,000,000, which may represent potential outliers or rare events that warrant further investigation. These high-revenue weeks could stem from unusual circumstances, such as special promotions, holiday seasons, or significant market shifts.

@@

```{r}
#| label: fig-yearly
#| fig-cap: Yearly Gross Revenue Trends for Broadway Productions, spanning from 2010 to 2019. Average yearly gross revenue remained relatively stable between 2013 and 2015. Outside of this period, the industry experienced growth. 
#| echo: false
#| warning: false
#| message: false

@@

# Create the plot
ggplot(data_yearly, aes(x = year, y = average_weekly_gross)) +
  geom_line(color = "steelblue", size = 1) +
  labs(
    x = "Year",
    y = "Average Yearly Gross ($)"
  ) +
  theme_minimal() +
  scale_x_continuous(  # Adjust scale for years
    breaks = seq(min(data_yearly$year), max(data_yearly$year), by = 1),  # One tick per year
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.subtitle = element_text(hjust = 0.5, size = 12)
  )

@@

```{r}
#| label: fig-week_ending
#| fig-cap: Weekly gross for each Broadway show over time, spanning from 2010 to 2019. Each point represents the gross for a particular week for a specific show. Most productions have weekly gross revenues ranging from $300,000 to $2,000,000, though the data becomes more scattered in later years. 
#| echo: false
#| warning: false
#| message: false

@@

```
@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with the results shown in @fig-weekly_gross. However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.

@@

```{r}
#| label: fig-avg_ticket_price
#| fig-cap: The distribution of average Broadway ticket prices shows that most prices cluster around $100, with a few shows exceeding $500.
#| echo: false

@@

```{r}
#| label: fig-seats_in_theatre
#| fig-cap: Distribution of Theatre Sizes Based on Number of Seats. Most productions are held in theaters with seating capacities around 1,200. However, there is considerable variation in theater size choices across different productions.
#| echo: false

@@

```{r}
#| label: fig-performances
#| fig-cap: Distribution of Performances. Over 10,000 weeks of shows, most productions adhere to the standard schedule of 8 performances per week. Only a small portion of productions deviate from this, with either more or fewer performances in a given week.
#| echo: false

@@

```{r}
#| label: fig-holiday_week
#| fig-cap: Comparison of Average Weekly Gross Between Holiday and Non-Holiday Weeks. This indicates that holiday weeks tend to result in higher weekly gross revenues for Broadway compared to non-holiday weeks.
#| echo: false

@@

# Bar chart for average weekly gross
ggplot(aggregated_data_holiday, aes(x = holiday_week, y = avg_weekly_gross, fill = holiday_week)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```
The Holiday Weeks was identified based on the major holidays of the year, as referenced in @stanley2013america, and includes the following:

- New Year’s Week: The week containing January 1st.
- Independence Day Week: The week of July 4th.
- Labor Day Week: The week containing Labor Day, which falls on the first Monday of September.
- Thanksgiving Week: The week containing the fourth Thursday of November.
- Christmas Week: The week containing December 25th.
- New Year's Week: The week of the January 1st.

Non-holiday weeks are defined as all other weeks that do not overlap with these predefined holiday periods. In addition, the average weekly gross revenue for each category was was calculated by summing all weekly gross revenues within the category and dividing by the total number of weeks in that category.

@@

```{r}
#| label: fig-Tony_Award
#| fig-cap: Comparison of Weekly Gross Revenue During Tony Award and Non-Award Months. This indicates that the occurrence of the Tony Awards in a given month does not significantly impact Broadway gross revenues.
#| echo: false

@@

# Bar chart for average weekly gross
ggplot(aggregated_data_award, aes(x = Tony_Award, y = avg_weekly_gross, fill = Tony_Award)) +
  geom_bar(stat = "identity", color = "black", alpha = 0.8) +  # Bar chart for aggregated data
  scale_fill_manual(values = c("darkorange", "#9F86C0")) +  # Custom colors for holiday and non-holiday
  labs(
    title = "Average Weekly Gross for Holiday vs Non-Holiday Weeks",
    x = "Week Type",
    y = "Average Weekly Gross ($)",
    fill = "Holiday Week"
  ) +
  scale_y_continuous(labels = scales::comma) +  # Add commas to the y-axis for readability
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none"  # Remove legend since x-axis already specifies week types
  )
```

According to @hodge202021st, the Tony Awards, established in 1947 by the American Theatre Wing, are Broadway’s highest honors, held annually in June. The "Best Musical" award is the most prestigious, significantly enhancing a production's success, with nominees 60% less likely to close and winners three times more likely to remain open, solidifying its status as the pinnacle of Broadway achievement.

@@

The objective of this study is to assist Broadway in strategically managing and making decisions to increase gross revenue, making it essential to choose a model that accurately explains the factors influencing revenue. To achieve this goal, several models were evaluated before selecting the final approach, including simple linear regression, decision trees, and multiple linear regression, each with its own strengths and weaknesses.

@@

Background details and diagnostics are included in [Appendix -@sec-model].

@@

- Intercept ($\beta_0$): Represents the predicted value of the weekly gross revenue when all predictors are 0. Since it is unrealistic for all predictors the intercept serves as a theoretical starting point for the model. 
- Average Ticket Price ($\beta_1$): Measures the change in weekly gross revenue for each one-dollar increase in average ticket price, assuming all other predictors remain constant.
- Seats in the Theater ($\beta_2$): Represents the additional revenue generated by each additional seat available in the theater, assuming all other factors remain constant.
- Number of Performances ($\beta_3$): Indicates the increase in weekly gross revenue for each additional performance in the week for the show, controlling for other variables.
- Holiday Week ($\beta_4$): Quantifies the difference in weekly gross revenue between holiday weeks and non-holiday weeks, all else being equal.
- Tony Award Month ($\beta_5$): Captures the difference in weekly gross revenue between weeks during the Tony Award month and other months, assuming other predictors remain unchanged.
- Year ($\beta_6$): Reflects the annual trend, representing the average change in weekly gross revenue for each one-year increase, controlling for other variables.

@@

As anticipated, average ticket price, seating in theater, and number of performances exhibit significant positive relationships with weekly gross revenue. Specifically, increases in ticket prices and theater size lead to higher gross revenue, consistent with the notion that larger venues and premium ticketing contribute to revenue growth. Similarly, the significant positive impact of the number of performances aligns with our expectation that additional shows increase overall revenue by accommodating more audiences.

@@

## Prioritizing Per-Seat Value Over Expanding Seating Capacity

While increasing seating capacity and performance frequency predictably boosts revenue, the marginal gains from these factors differ significantly depending on audience demand and pricing strategy. The revenue per additional seat, estimated at $699.82, is substantially lower than the per-show contribution of $70,688.48 or the impact of a $1 increase in ticket price, which generates $9,168. This result reflects that simply increasing seating capacity, without addressing demand or ticket pricing, offers limited revenue gains. The impact of additional seats becomes most meaningful only when shows consistently sell out, underscoring the importance of strategies that drive full occupancy.

The balance between ticket price and capacity is particularly significant, as a smaller venue with higher ticket prices can outperform a larger theater with lower-priced tickets. For instance, @leslie2004price demonstrates that optimizing ticket prices across seating sections can generate substantial revenue, often surpassing strategies focused solely on increasing seating capacity. Initiatives such as offering premium seating with added amenities, backstage tours, or bundled packages that include dining and entertainment can further enhance revenue while improving the audience experience. As emphasized by @ozhegova2018heterogeneity, understanding demand elasticity is essential, as premium seating typically exhibits lower price sensitivity, making it a key factor in strategic pricing decisions.

## Maximizing Holiday Demand

The model results show that holiday weeks increase weekly gross revenue by an average of $16,684, reflecting a notable seasonal boost and aligning with expectations of higher audience availability during festive periods. Holiday weeks are a time when families often travel or plan special outings, and New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, bustling holiday markets, and the New Year’s Eve Ball Drop in Times Square. This festive atmosphere draws millions of tourists. However, the relatively modest increase of $16,684 per week suggests that Broadway may not be fully capitalizing on its unique position as a holiday destination. Studies on tourist behavior during holidays indicate that travelers are more inclined to seek unique and memorable experiences during festive periods [@pearce2013minds], creating a prime opportunity for Broadway to enhance its gross revenue and establish itself as a must-visit holiday experience.

To better take advantage of its location and the influx of holiday visitors, Broadway could implement targeted strategies to make attending shows more convenient and appealing. Collaborating with hotels, travel agencies, and tourism boards to offer bundled holiday packages that include show tickets could position Broadway as an essential part of visitors’ holiday itineraries. Moreover, enhancing the on-site experience with seasonal concessions, festive decor, and exclusive holiday merchandise could create a more engaging and memorable experience, attracting more visitors and driving additional revenue during this lucrative season.

## Transforming the Tony Awards as an Industry-Wide Opportunity

Tony Award months show a negligible or slightly negative impact on overall revenue, with an estimated effect of $-7,140, challenging the assumption that the awards season boosts Broadway’s financial performance. However, @boyle2009broadway finds that Tony Awards increase a production’s revenue by 12% in the week immediately following the event. This discrepancy likely stems from media attention and ticket sales being concentrated on a few nominated or winning shows, while most productions see little benefit. Additionally, @reddy1998exploring highlights the significant role of critics’ reviews in driving Broadway success, further emphasizing the missed opportunity to leverage the publicity generated by the Tony Awards to benefit all productions more broadly.

Thus, Broadway could transform the Tony Awards into an industry-wide promotional platform by adopting strategies that engage a broader audience and distribute the benefits more equitably, extending beyond just the nominated and award-winning productions. Collaborating with media outlets to produce exclusive behind-the-scenes content, interviews with nominees, and live coverage of performances from non-nominated shows could help expand the appeal of the awards season. Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue. Centralized marketing campaigns emphasizing the diversity and vibrancy of Broadway’s offerings during this period could further drive engagement and ticket sales across the ecosystem. By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.

@@

Additionally, the model assumes uniform effects of predictors across all Broadway shows, which may oversimplify the analysis. Different types of productions (e.g., musicals, plays, blockbusters, or niche shows) likely have distinct revenue dynamics that are not adequately addressed by a single model. 
Moreover, the model does not account for external factors such as economic conditions, competitor pricing, or shifts in tourism trends, all of which could significantly influence Broadway revenue. These omissions limit the model's ability to fully explain variations in weekly gross revenue and highlight areas for future improvement.

@@

@@

The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection. You can access the survey at the following link: [Google Form Survey](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)

@@

In addition to the dataset used for this study, Broadway conducts several key surveys to collect detailed information on various aspects of Broadway theater. However, the information and datasets collected through these surveys are not publicly accessible for analysis. If this data were made available, merging it with the current dataset could provide a more robust model for gross analysis. These surveys include **The Demographics of the Broadway Audience** [@broadway_demographics_2022], designed to analyze the composition and behavior of Broadway theatergoers.

@@

Broadway also records and analyzes additional information, such as Broadway's Economic Contribution to New York City, the Audience for Touring Broadway, and the Economic Impact of Touring Broadway [@broadway_research_reports]. These surveys and studies provide a broader understanding of Broadway's influence and reach, offering a more complete view of its cultural and economic significance.
